---
title: "11/25 Practice"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(rvest)
library(stringr)
library(janitor)
library(dplyr)
library(fs)
library(robotstxt)
library(httr)
library(httr2)
library(jsonlite)
library(knitr)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r cars}
url <- "https://books.toscrape.com/index.html"
url_p <- read_html(url)

titles <- url_p |> 
  html_elements(xpath = "//article[@class='product_pod']/h3/a") |>
  html_attr("title")

prices <- url_p |>
  html_elements(xpath = "//article[@class='product_pod']/h3/div[@class='product_price']/p[@class='price_color']") |>
  html_text2()

rating <- url_p |>
  html_elements(xpath = "//article[@class='product_pod']/p[contains(@class, 'star-rating')]") |>
  html_attr("title") |>
  str_replace("star-rating", "") |>
  factor(levels = c("One", "Two", "Three", "Four", "Five"), labels = 1:5)

book_links <- url_p |>
  html_elements(xpath = "//article[@class='product_pod']/h3/a") |>
  html_attr("href") |>
  paste0("https://books.toscrape.com/", .)

get_stock <- function(link) {
  book_page <- read_html(url)
  stock_text <- book_page |>
    html_element(xpath = "//table[@class='table table-striped']/tr[th[text()='Availability']]/td") |>
    html_text2()
  stock_no <- str_extract(stock_text, "\\d+")
  return(as.integer(stock_no))
}

stock <- map_int(book_links, get_stock)

df <- data.frame(
  Title = titles,
  Price = prices,
  Rating = ratings,
  Stock = stock
)


```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
